\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-07 doc/USER_MANUAL/manual_SPECFEM3D.tex
updated both manuals (added reference to Oliveira and Seriani, also to Fichtner et al.)

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
Note that in many (most?) geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.

Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08}.

@@

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
The next release will use the PT-Scotch parallel library for mesh partitioning.

@@

The SPECFEM3D software package relies on the Scotch library to partition the meshes created with CUBIT.
Note that we use CUBIT to create meshes of hexahedra, but other packages can be used as well, for instance GiD from http://gid.cimne.upc.es, Gmsh from http://geuz.org/gmsh or even TetGen from http://tetgen.berlios.de (TetGen generates tetrahedra, but each of them can easily be decomposed into four hexahedra as shown in the picture of the TetGen logo at http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif ).

>>>>

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
In particular, it can accurately handle very distorted mesh elements \citep{OlSe11}.
Note that in many (most?) geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.

Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08,FiIgBuKe09}.

@@

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10,Kom11}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
The next release will use the PT-Scotch parallel library for mesh partitioning.

@@

The SPECFEM3D software package relies on the Scotch library to partition the meshes created with CUBIT.
Note that we use CUBIT to create meshes of hexahedra, but other packages can be used as well, for instance GiD from http://gid.cimne.upc.es or Gmsh from http://geuz.org/gmsh. Even mesh creation packages that generate tetrahedra, for instance TetGen from http://tetgen.berlios.de, can be used because each tetrahedron can then easily be decomposed into four hexahedra as shown in the picture of the TetGen logo at http://tetgen.berlios.de/figs/Delaunay-Voronoi-3D.gif; while this approach does not generate hexahedra of optimal quality, it can ease mesh creation in some situations and it has been shown that the spectral-element method can very accurately handle distorted mesh elements \citep{OlSe11}.
